Verifying Demonstrations

### 2018-02-28 paper/intro.tex
Fixes spacing and colons in intro desc environments

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility]: anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability]: anyone can verify that the result is according to the cast votes.
  \item[Individual verifiability]: every voter can verify that their vote is included in the result.
\end{description}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
We will define these more formally in \cref{Verifiability}.

There are also three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[VotePrivacy]: the voting does not reveal the individual vote.
  \item[ReceiptFreeness]: the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[CoercionResistance]: a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
\end{description}
We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do. 
%Seb: suggestion maybe we should put the following part in the discussion
However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness (see \cref{Privacy} for a detailed definition) is desired.
In essence, upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
%Sonja says: I'm confused: can we or can we not provide this?
%Seb: I agree with Sonja, it is not clear whether we achieve it or not

>>>>

Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{description}
  \item[Eligibility:] anyone can verify that each vote cast is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according 
    to the cast votes.
  \item[Individual verifiability:] every voter can verify that their vote is 
    included in the result.
\end{description}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.
We will define these more formally in \cref{Verifiability}.

There are also three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{description}
  \item[Vote privacy:] the voting does not reveal the individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can 
    be used as a proof of how the voter voted.
  \item[Coercion pesistance:] a voter cannot cooperate with a coercer to prove 
    the vote was cast in any particular way.
\end{description}
We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do. 
%Seb: suggestion maybe we should put the following part in the discussion
However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
Thus we need at least participation-proof privacy but receipt freeness (see \cref{Privacy} for a detailed definition) is desired.
In essence, upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
%Sonja says: I'm confused: can we or can we not provide this?
%Seb: I agree with Sonja, it is not clear whether we achieve it or not
